Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-02-08 vertical-thermal-review.Rmd
marielle's suggestion

**Authors:** 
Nidhi Vinod^1,2^,
Martijn Slot^3^,
Ian R. McGregor^4^,
Elsa M. Ordway^2,5^,
Marielle N. Smith^6^,
Tyeen Taylor^7^,
Lawren Sack^2^,
Thomas N. Buckley^8^,
Kristina J. Anderson-Teixeira^1,3^*

@@

![**Figure `r fig_NEON_vertical`. Vertical gradients in the biophysical environment for six US forest sites in the National Ecological Observatory Network (NEON)**. Height profiles, normalized relative to the top of the canopy, are shown for: growing season (a) modelled leaf area density, (b) calculated proportion of sun leaves, and (c) proportion light incident to the top of the canopy (as fraction relative to to top of canopy), and for July mean ± 1 standard deviation for (d) maximum photosynthetically active radiation (PAR), (e) maximum wind speed, (f) minimum humidity (min RH), (g) maximum air temperature ($T_{air}$), and (h) maximum biological temperature, ($T_{bio}$). Measurements extend from ground level (normalized height = 0 m) to the top of the canopy (horizontal dashed line at normalized height = 1) or above (d-g). Sites, which represent a variety of forest structures, include a mixed northern hardwood forest (Harvard Forest, MA; HARV), a subtropical longleaf pine savanna (Ordway-Swisher Biological Station, FL; OSBS), a tropical montane broadleaf evergreen forest (Pu'u Maka'ala Natural Area Reserve, Hawai'i; PUUM), two temperate broadleaf forests (Smithsonian Conservation Biology Institute, VA, SCBI; Smithsonian Environmental Research Center, MD, SERC), and a coniferous forest (Wind River Experimental Forests, WA; WREF). Further site information is given in Supporting Information Table `r NEON_sites`, and analysis details in Supporting Information Methods `r appendix_NEON_methods`. Vertical profiles in micrometeorological variables (d-h) at all forested NEON sites are shown in Supporting Information Figure `r SIfig_NEON_all`.](NEON_height_profiles/figures/Fig2_normalized.png)

>>>>

**Authors:** 
Nidhi Vinod^1,2^,
Martijn Slot^3^,
Ian R. McGregor^4^,
Elsa M. Ordway^2,5^,
Marielle N. Smith^6^,
Tyeen C. Taylor^7^,
Lawren Sack^2^,
Thomas N. Buckley^8^,
Kristina J. Anderson-Teixeira^1,3^*

@@

![**Figure `r fig_NEON_vertical`. Vertical gradients in the biophysical environment for six US forest sites in the National Ecological Observatory Network (NEON)**. Height profiles, normalized relative to the top of the canopy, are shown for: growing season (a) modelled leaf area density, (b) estimated proportion of sun leaves, and (c) proportion of light incident to the top of the canopy (as fraction relative to to top of canopy), and for July mean ± 1 standard deviation for (d) maximum photosynthetically active radiation (PAR), (e) maximum wind speed, (f) minimum humidity (min RH), (g) maximum air temperature ($T_{air}$), and (h) maximum biological temperature, ($T_{bio}$). Measurements extend from ground level (normalized height = 0 m) to the top of the canopy (horizontal dashed line at normalized height = 1) or above (d-g). Variables shown in panels a-c are derived from lidar, and those shown in panels d-h from micrometeorological tower data. Sites, which represent a variety of forest structures, include a mixed northern hardwood forest (Harvard Forest, MA; HARV), a subtropical longleaf pine savanna (Ordway-Swisher Biological Station, FL; OSBS), a tropical montane broadleaf evergreen forest (Pu'u Maka'ala Natural Area Reserve, Hawai'i; PUUM), two temperate broadleaf forests (Smithsonian Conservation Biology Institute, VA, SCBI; Smithsonian Environmental Research Center, MD, SERC), and a coniferous forest (Wind River Experimental Forests, WA; WREF). Further site information is given in Supporting Information Table `r NEON_sites`, and analysis details in Supporting Information Methods `r appendix_NEON_methods`. Vertical profiles in micrometeorological variables (d-h) at all forested NEON sites are shown in Supporting Information Figure `r SIfig_NEON_all`.](NEON_height_profiles/figures/Fig2_normalized.png)
